The hydra and the rooster

### 2020-07-10 latex/chapter-skippable.tex
better definoition of Ipred

We say also that $\alpha$ is the \emph{limit} of the sequence $\textit{fin}\;i, i\in\mathbb{N}$, according to the followi,g definition (in~\href{../src/html/hydras.Prelude.Ordinal-generic.html}{Prelude.Ordinal\_generic}).
$\alpha$ is the $\omega$-limit of the sequence $s$ if $\alpha$ is [strictly] larger than all the $s(i)$, and for any
$\beta<\alpha$, $\beta$ is dimonated by at least an element of  the sequence $s$ (in fact $\beta$ is dominated by an infinite number of elements of the sequence (\emph{exercise!})).

@@

>>>>

\subsection{Limit and successor ordinals}

\index{Maths!Limit ordinals}

We say also that $\omega$ is the \emph{limit} of the sequence $\textit{fin}\;i, i\in\mathbb{N}$, according to the followi,g definition (in~\href{../src/html/hydras.Prelude.Ordinal_generic.html}{Prelude.Ordinal\_generic}).
$\alpha$ is the $\omega$-limit of the sequence $s$ if $\alpha$ is [strictly] larger than all the $s(i)$, and for any
$\beta<\alpha$, $\beta$ is dimonated by at least an element of  the sequence $s$ (in fact $\beta$ is dominated by an infinite number of elements of the sequence (\emph{exercise!})).

@@

\index{Exercises}

\begin{exercise}
Prove that $\omega$ is the unique   limit ordinal \emph{(in this precise notation system! In larger segments of ordinal, there will be \emph{a lot} of limit ordinals}).
\end{exercise}

Let $\alpha$ and $\beta$ be some ordinals, we say that \emph{$\alpha$ is an immediate predecessor of $\beta$}
(or that \emph{$\beta$ is a  successor of $\alpha$ }) if $\alpha<\$beta$ and there is no ordinal $\gamma$ between $\alpha$ and $\gamma$.

\noindent\emph{From Module~\href{../src/html/hydras.Prelude.Ordinal_generic.html}{Prelude.Ordinal\_generic}}

\begin{Coqsrc}
Definition Ipred {A:Type}{lt : relation A}
           {sto : StrictOrder lt} (x y : A):=
  lt x y /\ (forall z,  lt z y -> clos_refl _ lt z x).

Definition Successor {A:Type}{lt : relation A}
           {sto : StrictOrder lt} (y x : A):= Ipred x y.
\end{Coqsrc}
